Data Dashboard

### 2020-01-23 analysis/05_market_simulator.Rmd
Loaded in the incercept model and got the means for the data, next we need to: 1. drop missing variables for the inputs 2. set up the matrix multiplication for the betas 3. set the inputs to work with

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
```

>>>>

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
library(here)
```

```{r load data}
intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))
